---
title: "p8105_hw5_yc3242"
author: "Youn Kyeong Chang (uni# yc3242)"
date: "November 7, 2018"
output: github_document
---

```{r}
library(tidyverse)
```

### Problem 1

#### 1-(1)
: Create a tidy dataframe containing data from all pariticipants, including the subject ID, arm, and observations over time.

```{r load_study_data, message = FALSE}
# Started with a dataframe containing all file names
study_data = 
  tibble(file_names = list.files(path = "data/", full.names = T))

# Iterated over file names and read in data for each subject and saved them as a data variable in the dataframe
study_data$data =
  map(study_data$file_names, read_csv)

# Tidied data 
study_data =
  study_data %>% 
  unnest() %>% 
  separate(file_names, into = c("arm", "id"), sep = "_") %>% 
  mutate(arm = str_remove(arm, "data/"),
         id = str_remove(id, ".csv")) %>% 
  gather(key = "week", value = "obs", "week_1":"week_8") %>% 
  mutate(week = as.numeric(str_remove(week, "week_")))
```

#### 1-(2)
: Spaghetti plot showing observations on each subject over time.

```{r plot_study_data}
study_data %>% 
  ggplot(aes(x = week, y = obs, group = id)) +
  geom_line(aes(color = arm), size = 1) +
  labs(
    title = "Observations on each subject over time",
    y = "observation"
  ) +
  facet_grid(~ arm) +
  stat_summary(aes(group = arm), fun.y = "mean", geom = "point", 
               color = "blue", size = 3, shape = 17) +
  theme_bw() +
  theme(plot.title = element_text(size = 12),
        strip.background = element_rect(fill = "black"),
        strip.text = element_text(color = "white", face = "bold")) 
```


Average observation is similar at starting point week 0 but over time, average observation in control group remains constant while in exosure group is increasing. 

### Problem 2

#### 2-(1) 
: load and describe raw data.

```{r homicide_data_load}
homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names()
```

The data consists of `r nrow(homicide_data)` observations and `r ncol(homicide_data)` variables as follows:

- `uid`: report identifier
- `reported_date`: reported date
- `victim_last`: Last name of victim
- `victim_first`: First name of victim
- `victim_race`: Race of victim
- `victim_age`: Age of victim
- `victim_sex`: Sex of victim
- `city`: city of homicide
- `state`: State of homicide 
- `lat`: latitude of homicide 
- `lon`: longitude of homicide 
- `disposition`: Case classification

#### 2-(2)
: Create a `city_state` variable.

```{r city_state}
homicide_data = 
  homicide_data %>% 
  unite(city_state, city, state, sep = ",") %>% 
  mutate(city_state = recode(city_state, "Tulsa,AL" = "Tulsa,OK")) 
```

#### 2-(3)
: Total number of homicide and the number of unsolved homicides.

```{r}
ttl_unsol = 
homicide_data %>%
  group_by(city_state) %>% 
  summarize(total = n(), 
            unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))

ttl_unsol
```

#### 2-(4)
: For the city of Baltimore, MD, estimate the proportion of homicides that are unsolved.
```{r}
# ttl_unsol only for Baltimore,MD
ttl_unsol_balti = 
  ttl_unsol %>% 
  filter(city_state == "Baltimore,MD") 

# Prop.test
balti_prop = 
  prop.test(ttl_unsol_balti$unsolved, ttl_unsol_balti$total)

balti_prop

# Dataframe
balti_prop_df =
  balti_prop %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)

balti_prop_df
```


###2-(5)
: proportion of unsolved homicides for each of the cities

```{r}
prop_unsol = 
  ttl_unsol %>% 
  mutate(test_res = map2(unsolved, total, prop.test)) %>% 
  mutate(est_CI = map(test_res, broom::tidy)) %>% 
  select(city_state, est_CI) %>% 
  unnest() %>% 
  select(city_state,estimate, conf.low, conf.high)

prop_unsol
```


###2-(6)
: Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

```{r prop_unsol_plot, fig.height = 7}
prop_unsol %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), color = "darkred") + 
  coord_flip() + 
  labs(title = "Proportion of unsolved cases for each city",
       subtitle = "Error bar using mean as center with 95% CIs",
       y = "Proportion of unsolved cases", 
       x = "City") +
  theme_bw()
```

